Using pressure-driven flow systems to evaluate laser speckle contrast imaging

### 2022-07-06 article.tex
Edits from Andy and Adam

\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{tocloft}
\usepackage[version=4]{mhchem}
\usepackage{booktabs}
\usepackage{blindtext}
\usepackage{xcolor}

@@

\abstractsection{Significance}
Microfluidic phantom studies are commonly used for characterizing the performance of laser speckle contrast imaging (LSCI) instruments. The selection of the flow control system is critical for the reliable generation of flow during testing. The majority of recent LSCI studies using microfluidics used syringe pumps for flow control.

@@

\abstractsection{Results}
The pressure-regulated flow system produced much more stable and reproducible flow outputs compared to the syringe pump. The expanded uncertainty for the syringe pump was 8--20$\times$ higher than that of the pressure-regulated flow system across the tested flow speeds \textcolor{red}{(Should we use exact numbers here? If so, which flow speeds?)}. Using the pressure-regulated flow system, MESI outperformed single-exposure LSCI at all flow speeds and closely mirrored the flow sensor measurements, with average errors of 4.6\% and 15.7\%, respectively \textcolor{red}{(Include $\pm$ std too?)}.

@@

Syringe pumps are the most widely used flow control system in microfluidic studies and are believed to provide a highly-controlled flow output. A survey of over 20 LSCI studies using microfluidics that were published since 2015 found that syringe pumps were used in the majority (90\%) of experiments. The devices were from a variety of manufacturers and featured various syringe sizes and materials. Syringe pumps operate by applying mechanical force on the plunger of a syringe at a controlled speed. A rotating lead screw driven by a stepper motor controls the velocity of the plunger, which is calculated based on the syringe size and inner diameter to achieve a desired flow rate. However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Li:2014ca,Zeng.2014}. Syringe pumps have also been shown to have slow responsivity and can take a long time to achieve programmed flow rates \cite{Zhou:2011ey}. The trade-off between stability and responsivity makes it difficult \cite{Kang.2012} to obtain both stable flow and a fast flow response with a syringe pump system.

@@

In this paper, we address two primary objectives. First, we quantify the uncertainty in flow generation for both a syringe pump and pressure-regulated flow system. By understanding the real-world uncertainty associated with each flow controller, we can design a microfluidic study to characterize the performance of optical imaging techniques that minimizes the impact of flow-related errors. Secondly, we use the pressure-regulated flow system to assess the performance of both LSCI and MESI across a range of physiologically-relevant flow speeds. Using the inline flow sensor as reference, we demonstrate the superior accuracy of relative flow measurements with MESI compared to traditional single-exposure LSCI. Such measurements would have been confounded by the large uncertainties associated with syringe pump flow generation. The results of this study indicate that highly-accurate flow controllers, such as pressure-regulated flow systems, should be used when characterizing flow measurement techniques with microfluidic studies.

@@

\subsection{Microfluidic Phantom Fabrication}
\label{sect:methods_phantom}
The microfluidic flow phantom was cast using PDMS (Sylgard 184™, Dow Corning) with 1.8 mg titanium dioxide (\ce{TiO2}) added per gram of PDMS to generate a scattering background that mimics tissue optical properties ($\mu_s' = 8$ cm$^{-1}$) \cite{Parthasarathy:2008el,Yaroslavsky:2002tg}. The PDMS \ce{TiO2} mixture was vigorously mixed for 15 minutes to ensure even distribution of the \ce{TiO2} in the phantom. Centrifugation (3000 g relative centrifugal force, 10 minutes) was then performed to de-gas the sample and remove any \ce{TiO2} clumps.

@@

A colloidal mixture of suspended 1 $\mu$m diameter polystyrene microspheres (10\% w/w, 5100A, Thermo Fisher Scientific, Inc.) in ultra-filtered de-ionized (UFDI) water was used as a blood-mimicking solution. Based on Ref. \cite[]{Roggan:1999bz}, the reduced scattering coefficient ($\mu_s'$) of whole blood with hematocrit of 0.5 is approximately 20 cm$^{-1}$. By using a 7\% by volume mixture of the microsphere solution and UFDI water (e.g. 10 mL of blood mimicking solution = 0.7 mL of the 5100A solution + 9.3 mL UFDI water) we were able to achieve a calculated $\mu_s'$ of 19.8 cm$^{-1}$. However, we note that the anisotropy of the microsphere solution is different than that of whole blood ($g = 0.92$ versus $g = 0.98$). The blood-mimicking solution was preferred for several reasons: cleaning and safety, ease of acquisition, and because the flow sensor was factory-calibrated for deionized water. Since the concentration of microspheres was very low (0.7\% by weight in the final suspension), the water calibration of the flow sensor remained valid. The solution of microspheres was freshly mixed before each experiment to reduce particle aggregation. Once mixed, the solution was sonicated for 10 minutes to fully suspend the particles and then de-gassed under vacuum to eliminate air bubbles.

\subsection{Microfluidic Flow System Instrumentation}

@@

\subsection{LSCI Instrumentation}

A schematic of the LSCI setup is shown in Fig.~\ref{fig:system_lsci}a. Measurements were performed using a 660 nm laser diode (HL6545MG, Thorlabs Inc.) mounted in a temperature-controlled housing (LDM21, Thorlabs Inc.) and expanded using an aspheric lens to obliquely illuminate the microfluidic. The laser diode controller (LDC205C, Thorlabs, Inc.) was set to 200 mA ($\sim$120 mW) while the temperature controller (TED200C, Thorlabs Inc.) was set to 10.5 k$\Omega$ (23.8 $^\circ$C). A pair of fixed focal length consumer camera lenses (AF Nikkor 50 mm $f$/1.8D, Nikon Corp.) were placed in tandem with infinity focus for 1:1 imaging. The aperture of the lower lens was set to 
$f$/11 in order to properly sample the speckle pattern \cite{Kirkpatrick:2008ke} while the upper lens was left at its maximum size of $f$/1.8. A longpass red filter (600 nm, R-60, Edmund Optics, Inc.) was placed between the two lenses to filter stray background light. The scattered light was imaged with a CCD camera (piA640-210gm, 648 $\times$ 488 pixels, Basler AG) controlled using custom software written in C++. The full sensor array was used, resulting in a field-of-view of 4.8 $\times$ 3.6 mm. The camera exposure time was set to 0.5 ms 
and allowed to run at full speed, resulting in an effective acquisition rate of $\sim$150 frames-per-second (fps).

\subsection{LSCI Flow Measurements}
\label{sect:methods_lsci}

@@

By incorporating efficient processing techniques\cite{Tom:2008tg} into the acquisition software, speckle contrast images were computed, displayed, and saved in real-time. During post-processing, the average speckle contrast was extracted from each frame within a region centered in the microfluidic channel. This value was used to estimate the correlation time ($\tau_{c}$) of the speckle autocorrelation function, which is considered a more quantitative measure of flow \cite{Briers:1996kfa}. The averaged speckle contrast value at each timepoint was fitted for its corresponding $\tau_{c}$ using Eq. \ref{eq:lsci},
%
% Equation 5 - LSCI Equation
\begin{equation}
    \label{eq:lsci}
    K^2(T, \tau_{c}) = \beta\frac{e^{-2x}-1+2x}{2x^2}
\end{equation}

@@

\subsection{MESI Instrumentation}

@@

\subsection{MESI and LSCI Performance}

A stepped flow profile experiment was conducted using the pressure-regulated flow system to assess the performance of both MESI and LSCI. The flow profile consisted of 19 steps spanning 1 -- 10 mm/s in 0.5 mm/s increments. Each speed was maintained for two minutes with a total duration of 40 minutes, including brief periods of no flow (0 mm/s) at the beginning and end of the profile. MESI measurements were acquired continuously throughout the experiment at the maximum acquisition rate of the system ($\sim$2.5 fps). Single-exposure (0.5 ms) LSCI frames were extracted from the MESI dataset \textit{post hoc}. The initial rise of the first flow step was again used to synchronize the timing of the MESI/LSCI and flow sensor datasets. The experiment was repeated a total of four times across two days.

The raw intensity images were converted to speckle contrast images and the average value within the microfluidic channel extracted from each frame as described previously in Section \ref{sect:methods_lsci}. The average speckle contrast values from all fifteen exposure times were then fitted to the multi-exposure speckle visibility equation \cite{Parthasarathy:2008el} to obtain an estimate of $\tau_c$,
%
% Equation 6 - MESI Equation
\begin{equation}
    \label{eq:mesi}
    K^2(T,\tau_c) =
        \beta\rho^2\frac{e^{-2x} - 1 + 2x}{2x^2} +
        4\beta\rho(1 - \rho)\frac{e^{-x} - 1 + x}{x^2} +
        \nu
\end{equation}

@@

\subsection{Microfluidic Flow System Assessment}

@@

\subsection{LSCI Flow Measurements}

The comparison between the syringe pump and the pressure-regulated flow systems as measured with the inline flow sensor and single-exposure LSCI is shown in Fig.~\ref{fig:SvP-FS_LSCI}. The underlying data for both plots are the same as in Fig.~\ref{fig:SvP-FS}b but are normalized against the first flow step to permit comparison. The relative flow changes measured by LSCI closely track those of the flow sensor and corroborate the accuracy and stability issues seen with the syringe pump system. These results demonstrate that LSCI is capable of detecting similar changes as the commercial flow sensor when measuring relative flow changes up to double the baseline.

@@

\subsection{MESI and LSCI Performance}

The flow measurement performance assessment using the pressure-regulated flow system is shown in Fig.~\ref{fig:flow_mesi_lsci}. The relative flow measured by MESI and LSCI are plotted alongside the flow sensor measurements from a single trial in Fig.~\ref{fig:flow_mesi_lsci}a. All relative flows were calculated using the average of the first flow step (1 mm/s) as the baseline. Data for each flow step were pooled and averaged across all four trials to assess the overall performance as seen in Fig.~\ref{fig:flow_mesi_lsci}b. The coefficients of determination ($R^2$) for this averaged MESI and LSCI data relative to the flow sensor were 0.988 and 0.839, respectively. The concordance correlation coefficients ($\rho_c$), a metric designed to evaluate reproducibility \cite{Lin.1989}, were 0.994 and 0.908, respectively. These results demonstrate both strong agreement between MESI and the flow sensor measurements and that MESI outperforms LSCI across large changes in relative flow. \textcolor{red}{Address apparent differences in performance for LSCI between Figs. \ref{fig:SvP-FS_LSCI}b and \ref{fig:flow_mesi_lsci}? The flow at the 5 mm/s step is $\sim$1.93$\times$ the flow at the 2.5 mm/s step in Fig. \ref{fig:flow_mesi_lsci}. Not quite the near-perfect agreement we see in Fig. \ref{fig:SvP-FS_LSCI}b.}

@@

Almost all microfluidic studies used for characterizing LSCI and MESI systems have been performed using syringe pumps. This study corroborates previous work \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey} that has shown syringe pumps do not produce stable flow outputs and demonstrates that single-exposure LSCI is sensitive enough to detect the resulting flow anomalies. Compared to the syringe pump, the pressure-regulated flow system produced much more stable and reproducible flow outputs across all trials. Because microfluidic studies are commonly used to assess LSCI and MESI instrument performance, an unstable flow control system contributes additional noise to the measurements, making it more difficult to properly characterize a system. For example, the flow profiles in Fig. \ref{fig:SvP-FS} and the uncertainty analysis in Table \ref{tab:uncertainty_combined} show large errors and high variability within and across trials using the syringe pump. These instabilities in flow were caused entirely by the syringe pump, as independently validated using single-exposure LSCI in Fig. \ref{fig:SvP-FS_LSCI}a. Such instability would increase the uncertainty in the true performance of any instrument being evaluated. The same analysis shows that a more reliable flow controller, such as the pressure-regulated flow system, produces minimal error and much improved reproducibility, therefore facilitating a more robust instrument assessment.

@@

The linearity of the results seen with both MESI and LSCI suggest that a calibration to absolute flow speeds might be feasible. However, any such calibration would be highly dependent upon experimental parameters, including the sample geometry (i.e. channel size), scatterer concentration, illumination configuration, and exposure time selection \textcolor{red}{(Any other major ones?)}. Changes to any of these parameters would produce different $ICT$ values, which would affect the correlation with the flow sensor and invalidate the calibration. It also remains to be seen whether calibrations performed in controlled microfluidic environments can reliably be translated to \textit{in vivo} measurements in animal or human subjects. \textcolor{red}{Should we elaborate further and give examples?}

>>>>

\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{tocloft}
\usepackage[version=4]{mhchem}
\usepackage{booktabs}

@@

\abstractsection{Significance}
Microfluidic flow phantom studies are commonly used for characterizing the performance of laser speckle contrast imaging (LSCI) instruments. The selection of the flow control system is critical for the reliable generation of flow during testing. The majority of recent LSCI studies using microfluidics used syringe pumps for flow control.

@@

\abstractsection{Results}
The pressure-regulated flow system produced much more stable and reproducible flow outputs compared to the syringe pump. The expanded uncertainty for the syringe pump was 8--20$\times$ higher than that of the pressure-regulated flow system across the tested flow speeds. Using the pressure-regulated flow system, MESI outperformed single-exposure LSCI at all flow speeds and closely mirrored the flow sensor measurements, with average errors of 4.6 $\pm$ 2.6\% and 15.7 $\pm$ 4.6\%, respectively.

@@

Syringe pumps are the most widely used flow control system in microfluidic studies and are believed to provide a highly-controlled flow output. A survey of over 20 LSCI studies using microfluidics that were published since 2015 found that syringe pumps were used in the majority (90\%) of experiments. The devices were from a variety of manufacturers and featured various syringe sizes and materials. Syringe pumps operate by applying mechanical force on the plunger of a syringe at a controlled speed. A rotating lead screw driven by a stepper motor controls the velocity of the plunger, which is calculated based on the syringe size and inner diameter to achieve a desired flow rate. However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Li:2014ca,Zeng.2014}. Syringe pumps have also been shown to have slow responsivity and can take a long time to achieve programmed flow rates \cite{Zhou:2011ey}. The trade-off between stability and responsivity makes it difficult \cite{Kang.2012} to obtain both stable flow and a fast flow response with a syringe pump system, both of which are necessary for LSCI characterization measurements.

@@

In this paper, we address two primary objectives. First, we quantify the uncertainty in flow generation for both a syringe pump and pressure-regulated flow system in microfluidic flow phantoms commonly used with optical blood flow imaging instruments. By understanding the real-world uncertainty associated with each flow controller, we can design a microfluidic study to characterize the performance of optical imaging techniques that minimizes the impact of flow-related errors. Secondly, we use the pressure-regulated flow system to assess the performance of both LSCI and MESI across a range of physiologically-relevant flow speeds. Using the inline flow sensor as reference, we demonstrate the superior accuracy of relative flow measurements with MESI compared to traditional single-exposure LSCI. Such measurements would have been confounded by the large uncertainties associated with syringe pump flow generation. The results of this study indicate that highly-accurate flow controllers, such as pressure-regulated flow systems, should be used when characterizing laser speckle techniques with microfluidic studies.

@@

\subsection{Microfluidic Phantom Fabrication}
\label{sect:methods_phantom}

The microfluidic flow phantom was cast using PDMS (Sylgard 184™, Dow Corning) with 1.8 mg titanium dioxide (\ce{TiO2}) added per gram of PDMS to generate a scattering background that mimics tissue optical properties at near infrared wavelengths ($\mu_s' = 8$ cm$^{-1}$) \cite{Parthasarathy:2008el,Yaroslavsky:2002tg}. The PDMS \ce{TiO2} mixture was vigorously mixed for 15 minutes to ensure even distribution of the \ce{TiO2} in the phantom. Centrifugation (3000 g relative centrifugal force, 10 minutes) was then performed to de-gas the sample and remove any \ce{TiO2} clumps.

@@

A colloidal mixture of suspended 1 $\mu$m diameter polystyrene microspheres (10\% w/w, 5100A, Thermo Fisher Scientific, Inc.) in ultra-filtered de-ionized (UFDI) water was used as a blood-mimicking solution. Based on Ref. \citen{Roggan:1999bz}, the reduced scattering coefficient ($\mu_s'$) of whole blood with hematocrit of 0.5 is approximately 20 cm$^{-1}$. By using a 7\% by volume mixture of the microsphere solution and UFDI water (e.g. 10 mL of blood mimicking solution = 0.7 mL of the 5100A solution + 9.3 mL UFDI water) we were able to achieve a calculated $\mu_s'$ of 19.8 cm$^{-1}$. However, we note that the anisotropy of the microsphere solution is different than that of whole blood ($g = 0.92$ versus $g = 0.98$). The blood-mimicking solution was preferred for several reasons: cleaning and safety, ease of acquisition, and because the flow sensor was factory-calibrated for deionized water. Since the concentration of microspheres was very low (0.7\% by weight in the final suspension), the water calibration of the flow sensor remained valid. The solution of microspheres was freshly mixed before each experiment to reduce particle aggregation. Once mixed, the solution was sonicated for 10 minutes to fully suspend the particles and then de-gassed under vacuum to eliminate air bubbles.

\subsection{Microfluidic Flow System Instrumentation}
\label{sect:methods_flow_system}

@@

\subsection{LSCI Instrumentation}
\label{sect:methods_lsci_system}

A schematic of the LSCI setup is shown in Fig.~\ref{fig:system_lsci}a. Measurements were performed using a 660 nm laser diode (HL6545MG, Thorlabs Inc.) mounted in a temperature-controlled housing (LDM21, Thorlabs Inc.) and expanded using an aspheric lens to obliquely illuminate the microfluidic. The laser diode controller (LDC205C, Thorlabs, Inc.) was set to 200 mA ($\sim$120 mW) while the temperature controller (TED200C, Thorlabs Inc.) was set to 10.5 k$\Omega$ (23.8 $^\circ$C). A pair of fixed focal length consumer camera lenses (AF Nikkor 50 mm $f$/1.8D, Nikon Corp.) were placed in tandem with infinity focus for 1:1 imaging. The aperture of the lower lens was set to 
$f$/11 in order to properly sample the speckle pattern \cite{Kirkpatrick:2008ke} while the upper lens was left at its maximum size of $f$/1.8. A longpass red filter (600 nm, R-60, Edmund Optics, Inc.) was placed between the two lenses to filter stray background light. The scattered light was imaged with a CCD camera (piA640-210gm, 648 $\times$ 488 pixels, Basler AG) controlled using custom software. The full sensor array was used, resulting in a field-of-view of 4.8 $\times$ 3.6 mm. The camera exposure time was set to 0.5 ms 
and allowed to run at full speed, resulting in an effective acquisition rate of $\sim$150 frames-per-second (fps).

\subsection{LSCI Flow Measurements}
\label{sect:methods_lsci_measure}

@@

During post-processing, the average speckle contrast was extracted from each frame within a region centered in the microfluidic channel. This value was used to estimate the correlation time ($\tau_{c}$) of the speckle autocorrelation function, which is considered a more quantitative measure of flow \cite{Briers:1996kfa}. The averaged speckle contrast value at each timepoint was fitted for its corresponding $\tau_{c}$ using Eq. \ref{eq:lsci},
%
% Equation 5 - LSCI Equation
\begin{equation}
    \label{eq:lsci}
    K^2(T, \tau_{c}) = \beta\frac{e^{-2x}-1+2x}{2x^2}
\end{equation}

@@

\subsection{MESI Instrumentation}
\label{sect:methods_mesi_system}

@@

\subsection{MESI and LSCI Performance}
\label{sect:methods_mesi_lsci_measure}

A stepped flow profile experiment was conducted using the pressure-regulated flow system to assess the performance of both MESI and LSCI using the same optical hardware. The flow profile consisted of 19 steps spanning 1 -- 10 mm/s in 0.5 mm/s increments. Each speed was maintained for two minutes with a total duration of 40 minutes, including brief periods of no flow (0 mm/s) at the beginning and end of the profile. MESI measurements were acquired continuously throughout the experiment at the maximum acquisition rate of the system ($\sim$2.5 fps). Single-exposure (0.5 ms) LSCI frames were extracted from the MESI dataset \textit{post hoc}. The initial rise of the first flow step was again used to synchronize the timing of the MESI/LSCI and flow sensor datasets. The experiment was repeated a total of four times across two days.

The raw intensity images were converted to speckle contrast images and the average value within the microfluidic channel extracted from each frame as described previously in Section \ref{sect:methods_lsci_measure}. The average speckle contrast values from all fifteen exposure times were then fitted to the multi-exposure speckle visibility equation \cite{Parthasarathy:2008el} to obtain an estimate of $\tau_c$,
%
% Equation 6 - MESI Equation
\begin{equation}
    \label{eq:mesi}
    K^2(T,\tau_c) =
        \beta\rho^2\frac{e^{-2x} - 1 + 2x}{2x^2} +
        4\beta\rho(1 - \rho)\frac{e^{-x} - 1 + x}{x^2} +
        \nu
\end{equation}

@@

\subsection{Microfluidic Flow System Assessment}
\label{sect:results_flow_assess}

@@

\subsection{LSCI Flow Measurements}
\label{sect:results_lsci_measure}

The comparison between the syringe pump and the pressure-regulated flow systems as measured with the inline flow sensor and single-exposure LSCI using the system described in Section \ref{sect:methods_lsci_system} is shown in Fig.~\ref{fig:SvP-FS_LSCI}. The underlying data for both plots are the same as in Fig.~\ref{fig:SvP-FS}b but are normalized against the first flow step to permit comparison. The relative flow changes measured by LSCI closely track those of the flow sensor and corroborate the accuracy and stability issues seen with the syringe pump system. These results demonstrate that LSCI is capable of detecting similar changes as the commercial flow sensor when measuring relative flow changes up to double the baseline.

@@

\subsection{MESI and LSCI Performance}
\label{sect:results_mesi_lsci_measure}

The flow measurement performance assessment using the pressure-regulated flow system is shown in Fig.~\ref{fig:flow_mesi_lsci}. The relative flow measured by MESI and LSCI using the system described in Section \ref{sect:methods_mesi_system} are plotted alongside the flow sensor measurements from a single trial in Fig.~\ref{fig:flow_mesi_lsci}a. All relative flows were calculated using the average of the first flow step (1 mm/s) as the baseline. Data for each flow step were pooled and averaged across all four trials to assess the overall performance as seen in Fig.~\ref{fig:flow_mesi_lsci}b. The coefficients of determination ($R^2$) for this averaged MESI and LSCI data relative to the flow sensor were 0.988 and 0.839, respectively. The concordance correlation coefficients ($\rho_c$), a metric designed to evaluate reproducibility \cite{Lin.1989}, were 0.994 and 0.908, respectively. These results demonstrate both strong agreement between MESI and the flow sensor measurements and that MESI outperforms LSCI across large changes in relative flow. \textcolor{red}{Address apparent differences in performance for LSCI between Figs. \ref{fig:SvP-FS_LSCI}b and \ref{fig:flow_mesi_lsci}? The flow at the 5 mm/s step is $\sim$1.93$\times$ the flow at the 2.5 mm/s step in Fig. \ref{fig:flow_mesi_lsci}. Not quite the near-perfect agreement we see in Fig. \ref{fig:SvP-FS_LSCI}b.}

@@

Almost all microfluidic studies used for characterizing LSCI and MESI systems have been performed using syringe pumps. This study corroborates previous work \cite{Li:2014ca,Zhou:2011ey,Zeng.2020} that has shown syringe pumps do not produce stable flow outputs and demonstrates that single-exposure LSCI is sensitive enough to detect the resulting flow anomalies (Fig. \ref{fig:SvP-FS_LSCI}). Furthermore, the close agreement between the LSCI and flow sensor demonstrates that these flow anomalies could be incorrectly interpreted as noise in the optical imaging system when they are actual flow variations. Compared to the syringe pump, the pressure-regulated flow system produced much more stable and reproducible flow outputs across all trials. Because microfluidic studies are commonly used to assess LSCI and MESI instrument performance, an unstable flow control system contributes additional noise to the measurements, making it more difficult to properly characterize a system. For example, the flow profiles in Fig. \ref{fig:SvP-FS} and the uncertainty analysis in Table \ref{tab:uncertainty_combined} show large errors and high variability within and across trials using the syringe pump. These instabilities in flow were caused entirely by the syringe pump, as independently validated using single-exposure LSCI in Fig. \ref{fig:SvP-FS_LSCI}a. Such instability would increase the uncertainty in the true performance of any instrument being evaluated. The same analysis shows that a more reliable flow controller, such as the pressure-regulated flow system, produces minimal error and much improved reproducibility, therefore facilitating a more robust instrument assessment.

@@

The linearity of the results seen with both MESI and LSCI suggest that a calibration to absolute flow speeds might be feasible. However, any such calibration would be highly dependent upon experimental parameters, including the sample geometry (i.e. channel size), scatterer concentration, illumination configuration, and exposure time selection. Changes to any of these parameters would produce different $ICT$ values, which would affect the correlation with the flow sensor and invalidate the calibration. It also remains to be seen whether calibrations performed in controlled microfluidic environments can reliably be translated to animal or human subjects since \textit{in vivo} measurements sample a range of different vessels \cite{Davis:2016ik,Jafari.2020}.
